Describe and Explore: Using feature-based time series clustering to identify meaningful structures in intensive longitudinal data

### 2023-01-20 methods-and-results.Rmd
:shit: formula tst

\begin{equation} \label{eq:ar}
  \frac{1}{(n-l)\sigma^2}\sum_{t=1}^{n-1}(X_t-\mu)(X_{t+l}-\mu) \\
  \frac{1}{(n-1)\sigma^2}\sum_{t=1}^{n-1}(X_t-\mu)(X_{t+1}-\mu)
\end{equation}

@@

summarized the nonlinear trend with the estimated degrees of freedom of an empty GAM spline model (edf) --- the edf summarizes the \textit{wiggliness} of the spline trend line.

>>>>

\begin{equation} \label{eq:ar}
  r_{ij,1} = \frac{\sum_{t=1}^{n-l}(x_{ijt}-\overline{x}_{ij})(x_{ijt-l}-\overline{x}_{ij})}{\sum_{t=1}^{n}(x_{ijt}-\overline{x}_{ij})^2}
\end{equation}

@@

\begin{equation} \label{eq:lin}
  b_{ij} = \frac{\sum(t-\overline{t})(x_{ijt}-\overline{x}_{ij})}{\sum(t-\overline{t})^2}
\end{equation}

summarized the nonlinear trend with the estimated degrees of freedom of an empty GAM spline model (edf) --- the edf summarizes the \textit{wiggliness} of the spline trend line. We estimate the number of parametric and non-parametric (or smooth) terms $p$ in the model.

\begin{equation} \label{eq:edf}
  edf \approx \sum p
\end{equation}

\textit{Notes}: In a Generalized Additive Model (GAM), the estimated degrees of freedom refers to the number of parameters used to estimate the model. This includes the number of parameters used to estimate each smooth function in the model, as well as any additional parameters used for the overall model.On the other hand, the effective degrees of freedom is a measure of the amount of information in the data that is used to estimate the model. It takes into account the smoothness of the estimated functions in the model, and is typically smaller than the estimated degrees of freedom. Effective degrees of freedom is used to estimate the uncertainty of the model estimates and to calculate the model's goodness of fit. In general, the effective degrees of freedom is a more appropriate measure of the complexity of the model than the estimated degrees of freedom, as it accounts for the smoothness of the estimated functions, which can help to prevent overfitting. This is because if the estimated function is smooth, it means that the model is not fitting the noise and has a better generalization.

### 2023-01-20 methods-and-results.tex
:shit: formula tst

summarized the nonlinear trend with the estimated degrees of freedom of
an empty GAM spline model (edf) --- the edf summarizes the
\textit{wiggliness} of the spline trend line.

>>>>

\begin{equation} \label{eq:lin}
  b_{ij} = \frac{\sum(t-\overline{t})(x_{ijt}-\overline{x}_{ij})}{\sum(t-\overline{t})^2}
\end{equation}

summarized the nonlinear trend with the estimated degrees of freedom of
an empty GAM spline model (edf) --- the edf summarizes the
\textit{wiggliness} of the spline trend line. We estimate the number of
parametric and non-parametric (or smooth) terms \(p\) in the model.

\begin{equation} \label{eq:edf}
  edf \approx \sum p
\end{equation}

\textit{Notes}: In a Generalized Additive Model (GAM), the estimated
degrees of freedom refers to the number of parameters used to estimate
the model. This includes the number of parameters used to estimate each
smooth function in the model, as well as any additional parameters used
for the overall model.On the other hand, the effective degrees of
freedom is a measure of the amount of information in the data that is
used to estimate the model. It takes into account the smoothness of the
estimated functions in the model, and is typically smaller than the
estimated degrees of freedom. Effective degrees of freedom is used to
estimate the uncertainty of the model estimates and to calculate the
model's goodness of fit. In general, the effective degrees of freedom is
a more appropriate measure of the complexity of the model than the
estimated degrees of freedom, as it accounts for the smoothness of the
estimated functions, which can help to prevent overfitting. This is
because if the estimated function is smooth, it means that the model is
not fitting the noise and has a better generalization.
